The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-04-24 paper/ms.tex
code description

\begin{equation}
    v_{x}=-\frac{y}{R}V_{\rm max}, \label{subeq1}
\end{equation}
\begin{equation}
    v_{y}=\frac{x}{R}V_{\rm max}, \label{subeq2}
\end{equation}
\begin{equation}
    v_{z}=0, \label{subeq3}
\end{equation}
%
where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear
velocity at the sphere's surface. The minus/plus sign in the
$x$/$y$-component of the velocity indicates the direction of
rotation. In this case we take the angular velocity in the same
direction as the $\hat{k}$ unit vector. With these definitions we can
write the angular velocity as $\omega=V_{\rm max}/R$.

@@

The photons are thus emitted in some region of the gas distribution
and follow a random walk in space and frequency until they escape the
gas distribution or are absorbed by a dust grain. The initialization
process for the \ly photons has to specify its position, frequency and
direction of propagation. In our case we select the initial frequency
to be exactly the \ly rest-frame frequency ($x=0$) and the direction of
propagation to be random following an flat probability distribution
over the sphere.

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.8\textwidth]{spectraCentral.eps}
\end{center}
\caption{Central.
    \label{fig:CentralSpec}}  
\end{figure*}

>>>>

\begin{equation}
    v_{x}=-\frac{y}{R}V_{\rm max}, \label{subeq1}
\end{equation}
\begin{equation}
    v_{y}=\frac{x}{R}V_{\rm max}, \label{subeq2}
\end{equation}
\begin{equation}
    v_{z}=0, \label{subeq3}
\end{equation}
%
where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear
velocity at the sphere's surface. The minus/plus sign in the
$x$/$y$-component of the velocity indicates the direction of
rotation. In this case we take the angular velocity in the same
direction as the $\hat{k}$ unit vector. With these definitions we can
write the norm of the angular velocity as $\omega=V_{\rm max}/R$.

@@

The photons are thus emitted in some region of the gas distribution
and follow a random walk in space and frequency until they escape the
gas distribution or are absorbed by a dust grain. The initialization
process for the \ly photons has to specify its position, frequency and
direction of propagation. In our case we select the initial frequency
to be exactly the \ly rest-frame frequency ($x=0$) and the direction of
propagation to be random following an flat probability distribution
over the sphere. A different initization that uses a Gaussian with a
velocity with equal to the thermal velocity, $12.8$\kms in our case,
should not introduce noticeable change given that our rotational
velocities span the range $100$-$300$\kms and the lines have velocity
widths on the order of $100$-$500$\kms.

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{spectraCentral.eps}
\end{center}
\caption{
2D histogram showing the number of photons that escape with frecuency
$x$ forming an angle $\theta$ (parameterized as $\cos\theta$) with the
rotationa axis. The rotational velocity ($0,100,200,300$\kms)
increases from left to right and the optical depth ($10^5$, $10^6$,
$10^7$) from top to bottom. 
\label{fig:CentralSpec} }   
\end{figure*}
